Campaign Contribution Limits and Corruption\\ Evidence from the 50 states

### 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.tex
Includes submitted JOPskeleton

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark Hand"
abstract: "Since its 1976 _Buckley v. Valeo_ decision, the Supreme Court has allowed only two potential justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. Do campaign finance limits actually mitigate corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the  Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper finds associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties. Individual donation limits, however, do not prove associated with either measure of corruption."
anonymized: true
output:
    draft::jop_submission:
        keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(MASS) # For binomial regression 
library(tidyverse) # everything; placed here because of MASS::select() overlap 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library(pglm) # For panel + binomial 
library(webshot) # For screenshots 
library(viridis) # For colorblindedness
library(GGally) # For ggpairs
library(lm.beta) # For standardized regression coefficients 
library(broom) # for augment()
library(devtools) # For downloading packages from github 
install_github("duckmayr/draft") # For JOP template 
theme_set(theme_classic()) # Sets default theme

```

```{r data import, eval=T, message=F, warning=F}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States" 
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("~/Documents/GitHub/Money-in-Politics/data/Replication/AltLassenJLEO.dta")

# Michael Barber's "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures"  
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")

# Data from ICC 
# www.greasethewheels.org/cci/
convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
```

```{r panel data wrangling,eval=T}
# Combining Barber and ICS  
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

BarberICC <- BarberICC %>% 
  mutate(
    ind_limits_dummy = ifelse(ind_limits_2010==99999,0,1),
    ind2pty_limits_dummy = ifelse(ind2pty_limits_2010==99999,0,1),
    pac_limits_dummy = ifelse(pac_limits_2010==99999,0,1),
    total_limits_dummy = ifelse(total_limits_2010==99999,0,1)
  )

# Adding AltLassen
# table(AltLassen$state_name)
AltLassen$state_name[AltLassen$state_name=="Californ"] = "California"
AltLassen$state_name[AltLassen$state_name=="Connecti"] = "Connecticut"
AltLassen$state_name[AltLassen$state_name=="Louisian"] = "Louisiana"
AltLassen$state_name[AltLassen$state_name=="Massachu"] = "Massachusetts"
AltLassen$state_name[AltLassen$state_name=="Minnesot"] = "Minnesota"
AltLassen$state_name[AltLassen$state_name=="Mississi"] = "Mississippi"
AltLassen$state_name[AltLassen$state_name=="NewHamps"] = "New Hampshire"
AltLassen$state_name[AltLassen$state_name=="NewJerse"] = "New Jersey"
AltLassen$state_name[AltLassen$state_name=="NewMexic"] = "New Mexico"
AltLassen$state_name[AltLassen$state_name=="NewYork"] = "New York"
AltLassen$state_name[AltLassen$state_name=="NorthCar"] = "North Carolina"
AltLassen$state_name[AltLassen$state_name=="NorthDak"] = "North Dakota"
AltLassen$state_name[AltLassen$state_name=="Pennsylv"] = "Pennsylvania"
AltLassen$state_name[AltLassen$state_name=="RhodeIsl"] = "Rhode Island"
AltLassen$state_name[AltLassen$state_name=="SouthCar"] = "South Carolina"
AltLassen$state_name[AltLassen$state_name=="SouthDak"] = "South Dakota"
AltLassen$state_name[AltLassen$state_name=="Tennesse"] = "Tennessee"
AltLassen$state_name[AltLassen$state_name=="Washingt"] = "Washington"
AltLassen$state_name[AltLassen$state_name=="WestVirg"] = "West Virginia"
AltLassen$state_name[AltLassen$state_name=="Wisconsi"] = "Wisconsin"
AltLassen$state_name <- state.abb[match(AltLassen$state_name,state.name)]
AltLassen <- AltLassen %>% 
  rename("st"="state_name")
AltLassen$year <-as.integer(AltLassen$year)

AltBarber <- inner_join(BarberICC, AltLassen)
```

@@

## Introduction
In 1976, the Supreme Court ruled in _Buckley v. Valeo_ that political campaign expenditures are the equivalent of free speech, and therefore protected by the first amendment. At the same time, the Court laid out one mechanism and two permissible reasons for limiting campaign contributions that enable those expenditures. First, it argued that more money contributed does not amount to “more” speech, allowing for the use of campaign contribution dollar amount limits. Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented. Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof. As Kang (2012) argues, the holdings in _Buckley v. Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades. Since _Buckley v. Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.

Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech. In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v. City of Berkeley_). Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v. Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v. Sorrell_, 2006).

The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups. In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election. Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban ( _FEC v. Wisconsin Right to Life_). Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v. FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions. One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v. Bennett_, 2011).

Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits. The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns. In _McCutcheon v. FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits. Another case, _Holmes v. FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections. In yet another, _Lair v. Mangan_ (2018), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.

The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, and the Fifth Circuit similarly upheld limits in Austin, TX (_Zimmerman v. City of Austin_, 2018). But further challenges to contribution limits are likely. Bopp said that he planned to appeal the Ninth Circuit’s ruling. Even if that fails, Bopp and other conservative groups plan to carry on. “I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech. Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).

## Prior Work 
Since the Buckley v. Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990). Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).

But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits. The scholarly research on corruption thus narrowly defined is mixed and heated. Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998). Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue. Other scholars, however, are not so convinced. Wright finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out (1990). And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).

As mentioned above, the Court is also interested in the appearance of corruption. On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002). Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009). And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).

One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counter-factual. Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence. Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level. Variation across states and over time allows room for studying the causes and consequences of campaign finance limits, separate from the question of corruption. Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006). As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.

A largely separate body of work has examined the causes and consequences of corruption at the state level, separate from campaign finance. Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014). Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013). They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).

@@

## Data and Design  
In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption. Given open debate about the proper measure of state-level corruption, I use two measures. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).

Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature. Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures. Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized. There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits. Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).

```{r Barber summary, eval=T,include=F}
# This is a summary, but includes all the 99999s and doesn't have skew in it.  
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

# This replaces all the 99999s. 
BarberNAs <- Barber %>% dplyr::na_if(99999)

# These are (highly skewed) histograms of the remaining values 
ind_limits_2010.plot <- ggplot(BarberNAs, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind2pty_limits_2010.plot <- ggplot(BarberNAs, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
pac_limits_2010.plot <- ggplot(BarberNAs, aes(pac_limits_2010)) + geom_density() + theme_minimal()

# How about correlations? Unclear what this shows us. 
# pairs(BarberNAs[3:6])

# An alternative, perhaps to combine if I can figure out how to print: 
# psych::describe(subset(BarberNAs[,3:6]))

# This is a summary table for all the state-years where limits exist:  
# stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
```

```{r Barber summary stats latex, results="asis",eval=T}
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F, 
          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
```

The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state. This measure of corruption is widely used in academic research, though not without criticism. Descriptive statistics for corruption convictions are included below.

The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions. The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).

```{r CRI summary latex, results="asis", eval=T}
stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)

# Next: How to demonstrate skew? # Test whether these are correlated? 
# ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
```

@@

This analysis has its limitations, beginning with the data sets themselves. Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI. The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index. They argue that the CCI includes only federal data; that the resources available to prosecutors varies from state to state; that US Attorneys are political appointees; and that the measure records only convictions, which is at best a reflection of underlying corruption.

The Corruption Reflections Index, too, has its flaws: It relies on a single news source, the Associated Press. Similar to federal prosecutors’ offices, the resources available to each AP office vary. It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a data set with an overall mean of 0.28 and standard deviation of 0.19. The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior. Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption, rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).

Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption. It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level. Third, it is also the case that campaign finance laws may not be equally enforced across states, even though the enforcement measures used here are from federal rather than state authorities.  Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}

\documentclass{jopsubmission}

%% Math support
\usepackage{amssymb} % Note: loads amsfonts
\usepackage{amsmath}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp} % provide euro and other symbols

% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\usepackage{float} % Noorah says this will help with \newpage in References 
\usepackage{xcolor}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
          hidelinks,
  pdfcreator={LaTeX via pandoc}}

\urlstyle{same} % disable monospaced font for URLs

%% For tables
\usepackage{booktabs}

%% For figures
\usepackage{graphicx}
\usepackage{adjustbox,lipsum} % Alternate to \resizebox, maybe? 
\usepackage{grffile}

\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% We don't want a date in there
\date{\vspace{-5ex}}

    \title{Campaign Contribution Limits and Corruption\\
Evidence from the 50 states}

% We need to remove section numbering
\setcounter{secnumdepth}{-\maxdimen}

\begin{document}

    \maketitle
            \begin{abstract}
        Since its 1976 \emph{Buckley v. Valeo} decision, the Supreme Court has
        allowed only two potential justifications for limiting campaign
        donations: To prevent corruption or the appearance of corruption. Do
        campaign finance limits actually mitigate corruption or its appearance?
        As current challenges to contribution limits wind their way through
        federal courts, the answer to this question will inform the Supreme
        Court's decision to uphold or strike down remaining limits on political
        campaign contributions. Using state-level data from 1990-2012 on
        contribution limits, corruption convictions, and media mentions of
        corruption, this paper finds associations between corruption convictions
        and the presence of limits on donations to political action committees
        (PACs), the amount of those limits, and the presence of limits on
        donations to parties. Individual donation limits, however, do not prove
        associated with either measure of corruption.
        \end{abstract}

@@

\subsection{Introduction}\label{introduction}

In 1976, the Supreme Court ruled in \emph{Buckley v. Valeo} that
political campaign expenditures are the equivalent of free speech, and
therefore protected by the first amendment. At the same time, the Court
laid out one mechanism and two permissible reasons for limiting campaign
contributions that enable those expenditures. First, it argued that more
money contributed does not amount to ``more'' speech, allowing for the
use of campaign contribution dollar amount limits. Donating one dollar
or \$5,000 to a political campaign amounts to a speech act, the Court
held, and so it is permissible to impose limits on the amount of
contributions as long as contributions are not prevented. Second, having
laid out this mechanism by which money in politics might be limited, the
court laid out only two constitutionally permissible reasons for
limiting contributions: To prevent corruption or the appearance thereof.
As Kang (2012) argues, the holdings in \emph{Buckley v. Valeo} provided
``the basic framework of contribution limits and disclosure
requirements'' for the following four decades. Since \emph{Buckley v.
Valeo}, Congress has passed only one campaign finance law, the
Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold,
the bill took aim at unlimited ``soft money'' contributions to political
parties and expanded the Federal Election Commission's disclosure
requirements to what it called ``electioneering communications,''
political ads not paid for by campaigns themselves.

Apart from McCain-Feingold, for forty years all changes in the landscape
of campaign finance have come from the Supreme Court and appellate
courts, which have worked to balance questions of corruption with those
of free speech. In 1981, the Court struck down contribution limits
related to ballot measures (\emph{Citizens against Rent Control v. City
of Berkeley}). Just before the passage of McCain-Feingold, the courts
considered state-level limits, allowing low limits in Missouri
(\emph{Nixon v. Shrink Missouri}, 2000), though it would later finding
Vermont's to be low enough that they had a meaningful impact on
political speech (\emph{Randall v. Sorrell}, 2006).

The passage of the McCain-Feingold in 2002 inspired a wave of challenges
to campaign contributions and expenditures, driven mostly by
conservative and religious political groups. In 2007, the Court examined
the McCain-Feingold ban on airing issue advertisements close to
election. Banning such ads, the Court argued, would have a chilling
effect on free speech, and it struck down the ban ( \emph{FEC v.
Wisconsin Right to Life}). Then, in 2010, the Court issued what has
become one of its most well-known rulings: In \emph{Citizens United v.
FEC} (2010), it struck down limits on independent expenditures by
outside groups, including corporations and unions. One critical aspect
of \emph{Citizens United} is the establishment of the principle that,
according to Justice Anthony Kennedy, ``independent expenditures do not
lead to, or create the appearance of, quid pro quo corruption.'' The
Court's emphasis on quid pro quo corruption as the only justification
for contribution limits extended the following year, as it struck down
an Arizona effort to level the political playing field with matching
state campaign funds (\emph{Arizona Free Enterprise Club v. Bennett},
2011).

Since 2011, the network of conservative legal groups behind Citizens
United has continued to take aim at contribution limits as an
unnecessary restriction of political speech, with a focus on individual
contribution limits. The 1971 Federal Election Campaign Act placed a
limit on the amount an individual could give to one campaign, in
addition to two-year limits on the total amount an individual could give
to political campaigns. In \emph{McCutcheon v. FEC} (2014) James Bopp,
one of the attorneys behind the Citizens United challenge, convinced the
Court of the unconstitutionality of total individual limits. Another
case, \emph{Holmes v. FEC} (2017), targeted the distribution of
individual campaign contribution across primary and general elections.
In yet another, \emph{Lair v. Mangan} (2018), Bopp once again took aim
at individual contribution limits, arguing that the state of Montana had
not shown compelling evidence that campaign contribution limits
decreased the risk of corruption.

The Ninth Circuit Court of Appeals upheld Montana's campaign
contribution limits, and the Fifth Circuit similarly upheld limits in
Austin, TX (\emph{Zimmerman v. City of Austin}, 2018). But further
challenges to contribution limits are likely. Bopp said that he planned
to appeal the Ninth Circuit's ruling. Even if that fails, Bopp and other
conservative groups plan to carry on. ``I handle a lot of cases,'' he
said after the 2014 McCutcheon ruling, ``and I`m not done yet.'' Supreme
Court Justice Clarence Thomas laid the groundwork for future challenges
in his commentary on the McCutcheon decision by arguing that more
dollars did, in fact, equate to more speech. Once established, that
principle supports the argument that campaign contribution dollar amount
limits are a potentially unconstitutional restriction on speech (Hurley
\& Debenedetti 2014, Zall 2017).

\subsection{Prior Work}\label{prior-work}

Since the Buckley v. Valeo decision, a wave of scholarship has taken
advantage of the campaign contribution data collected by the Federal
Election Commission to examine the causes and consequences of political
campaign contributions, including whether contributions buy access (not
to a meaningful degree, find Welch 1982 and Langbein 1986) and the
effectiveness of contributions relative to lobbying efforts (yes,
according to Wright 1990). Since the 2010 Citizens United and
speechnow.org decisions, another arm of scholarship has examined the
flows of money to groups engaging in independent expenditures (Spencer
and Wood 2014, Werner and Coleman 2014).

But lobbying, money for access, and independent expenditures all fall
outside of the narrow definition of quid pro corruption that the Supreme
Court considers a compelling enough state interest to justify campaign
contribution limits. The scholarly research on corruption thus narrowly
defined is mixed and heated. Stratmann finds evidence that donations
determined votes in at least one instance (1991); he also finds that the
timing of political action committees (PAC) donations suggests that
corporations believe those donations do affect legislators' votes
(1998). Reacting to the absence of evidence that donations lead to
favorable final votes on bills, Hall and Wayman (1990) look for and find
a positive relationship between political donations and the amount of
attention that legislators give to a particular issue. Other scholars,
however, are not so convinced. Wright finds that once lobbying efforts
are factored in, the effects of contributions on voting outcomes washes
out (1990). And it is notoriously difficult to tease out whether
political donations change legislators' minds or instead flow to
legislators with established, friendly positions (Ansolabehere et al
2003).

As mentioned above, the Court is also interested in the appearance of
corruption. On this score, results are more consonant: There seems to be
little association between campaign spending and public trust in
government (Primo 2002). Other factors, including media coverage of
campaign finance law and the professionalization of legislatures, are
more predictive of public perceptions of corruptions (Rosenson 2009).
And while the public does seem to report viewing campaign finance as a
contributor to corruption, there is not evidence that reform efforts
will have an effect on those views (Persily \& Lammie 2004).

One fundamental limitation of these federal level studies on campaign
contributions and corruption is the absence of a counter-factual. Given
that contribution limits have been in place since the 1970s, it is
difficult to argue what might have happened in their absence. Recent
work on campaign finance has attempted to address this problem by
focusing on the effects of differences in campaign finance laws at the
state level. Variation across states and over time allows room for
studying the causes and consequences of campaign finance limits,
separate from the question of corruption. Studies suggest that campaign
finance limits are associated with less electoral competition (Gross et
al 2002, Lott 2006), but that disclosure rules and some organizational
limits are associated with greater levels of government trust (Primo and
Milyo 2006) and may increase the return on campaign expenditures
(Stratmann 2006). As mentioned, Michael Barber's 2016 work finds that
lower limits on PAC donations relative to individual donations are
associated with higher polarization.

A largely separate body of work has examined the causes and consequences
of corruption at the state level, separate from campaign finance. Most
use the Department of Justice's Annual Public Integrity Report, which
correlate highly with state level perceptions of corruption (Walker and
Calcagno 2011, Glaeser and Saks 2006, Liu \& Mikesell 2014). Using that
data, researchers have found evidence that political corruption leads to
inflated state budgets and that the presence of casinos and subsequent
corruption (Liu \& Mikesell 2014, Walker \& Calcagno 2013). They have
also shown the absence of a link between state ethics commissions and
reduced corruption (Crider and Milyo 2013).

@@

\subsection{Data and Design}\label{data-and-design}

In this paper, I build upon the growing body of state-level political
science research to ask whether campaign contribution limits at the
state level associated with lower levels of corruption. Given open
debate about the proper measure of state-level corruption, I use two
measures. The first, a Corruptions Convictions Index, is the traditional
measure of state level corruption, built from Department of Justice
convictions data. The second, the Corruptions Reflection Index, is a new
measure put forward by Dincer and Johnston (2016). I combine these
measures with a third data set from Michael Barber's 2016 work on
campaign contribution limits and political polarization; and a fourth
data set from James Alt and David Dryer Lassen, to provide controls for
the full model (Alt and Lassen 2012).

Barber's data set is a panel of contribution limits from 1990-2012 for
the lower house of every state legislature. Barber compiled this data
set from the FEC, Westlaw, and the Nation Council of State Legislatures.
Each dollar amount is inflation indexed to 2010 dollar amounts, and
bi-annualized. There are three different types of limits in the Barber
database: Individual contribution limits, individual-to-party limits,
and PAC limits. Barber utilized individual and PAC contributions in his
analysis of polarization, leaving out individual-to-party limits given
that party contributions typically make up less than 10\% of total
political fundraising; I include it this analysis to determine whether
parties, rather than PACs or individuals, might be the locus of
corruption as measured by our other two data sets (Barber 2016).

% \begin{adjustbox}{max width=\textwidth}
\begin{table}[!htbp]\centering 
\caption{Descriptive Statistics for State Level Campaign Finance Limits} 
\label{} 
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Individual Limits & 802 & 3,801 & 4,236 & 143 & 827 & 5,078 & 23,164 \\ 
Individual-to-Party Limits & 472 & 33,222 & 45,732 & 834 & 7,243 & 32,882 & 196,470 \\ 
Party Limits & 543 & 23,804 & 32,616 & 246 & 5,246 & 24,976 & 150,904 \\ 
PAC Limits & 742 & 6,396 & 9,440 & 223 & 1,231 & 9,302 & 96,940 \\ 
\hline \\[-1.8ex] 
\multicolumn{8}{l}{Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present} \\ 
\end{tabular} 
}
\end{table}
% \end{adjustbox}

The second data set comes from the Department of Justice's ``Report to
Congress on the Activities and Operations of the Public Integrity
Section'' by way of the Institute for Corruption Studies.\footnote{N.B.
  According to one of the researchers'
  \href{https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx}{curricula
  vitae}, the Institute for Corruption Studies is funded in part by a
  grant from the Charles Koch Research Foundation. Organizations funded
  by Charles and David Koch are also funders of legal groups driving
  legal battles mentioned in the introduction, according to a
  \href{https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance}{report}
  by the Center for Public Integrity.} Since 1976, the FBI has tracked
political corruption at the state level, and the Corruption Convictions
Index (CCI) used here includes the number of corruption convictions in a
year normalized by the population in each state. This measure of
corruption is widely used in academic research, though not without
criticism. Descriptive statistics for corruption convictions are
included below.

The third data set is the Institute for Corruption Studies' Corruption
Reflections Index (CRI), put together by Dincer and Johnston for their
2016 article on state-level corruption, and which they create in
response to the limitations of the Corruption Convictions. The
Corruption Reflections Index represents the fraction of Associated Press
stories about politics in a particular state that mention political
corruption (Dincer and Johnston 2016).

\begin{table}[!htbp] \centering 
  \caption{Descriptive Statistics for Corruption and Reflections} 
  \label{} 
  \resizebox{\textwidth}{!}{%
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Corruption Convictions Index (CCI) & 1,999 & 2.96 & 2.99 & 0.00 & 1.03 & 3.97 & 33.85 \\ 
Corruption Reflections Index (CRI) & 1,887 & 0.28 & 0.19 & 0.00 & 0.15 & 0.37 & 2.16 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
}
\end{table}

@@

This analysis has its limitations, beginning with the data sets
themselves. Barber's state campaign contributions data lacks information
about upper houses of state legislatures, which are included in both the
CCI and CRI. The Corruption Convictions Index suffers from a number of
issues, as outlined by Dincer and Johnston in their introduction to the
Corruption Reflections Index. They argue that the CCI includes only
federal data; that the resources available to prosecutors varies from
state to state; that US Attorneys are political appointees; and that the
measure records only convictions, which is at best a reflection of
underlying corruption.

The Corruption Reflections Index, too, has its flaws: It relies on a
single news source, the Associated Press. Similar to federal
prosecutors' offices, the resources available to each AP office vary. It
also demonstrates high variation in the data; Utah, for example, has a
mean CRI score of 0.46 and standard deviation of 0.38, in a data set
with an overall mean of 0.28 and standard deviation of 0.19. The
Corruption Reflections Index also seems to assume in its name that media
reports of corruption are a mere reflection of corruption, rather than
an endogenous variable in the ecosystem that enables corrupt behavior.
Previous work, in contrast, has argued that media have a clear bias and
play an important role in shaping public perceptions of corruption,
rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and
Snyder 2005).

Most broadly, this analysis does not directly address the ``appearance
of corruption,'' the second of the Supreme Court's reasons for allowing
campaign contribution limits; to do so effectively would require time
series, state-level data specifically about quid pro quo corruption. It
is also the case that this analysis looks to the states intentionally in
order to address the issue of the counter-factual inherent in looking at
federal data, it may not be the case that statewide results are
generalizable to, or distinct from, what is occurring at the federal
level. Third, it is also the case that campaign finance laws may not be
equally enforced across states, even though the enforcement measures
used here are from federal rather than state authorities. Finally, the
period in question (1990-2004) is short enough that there may be some
factor that influences corruption arrest across a meaningful portion of
the data set.

\subsection{Methods}\label{methods}
